Supercritical fluid extraction of essential oil from chamomile flowers: modelling, and parameter estimation

### 2024-05-06 SFE_article_Parameter_Estimation_short_no_axial_diff- Chamomile/Sections/Model.tex
06.05

		\citet{Bulley1984} suggests a process where the driving force for extraction is given by the difference between the concentration of the solute in bulk, $c_f$, and in the center of the pore, $c_p^*$. The concentration $c_p^*$ is in equilibrium with $c_s$ according to an equilibrium relationship. The rate of extraction is thus $r_e\left(c_f - c^*_p(c_s)\right)$.

		On the other hand, \citet{Reverchon1996} proposes a driving force given by the difference between $c_s$ and $c_p^*$.Concentration $c_p^*$ is determined by an equilibrium relationship with $c_f$ and the extraction rate given by Equation \ref{Model_kinetic_basic}

@@

		where $\Theta$ is a paramter space, ${\color{black}\bar{\phi}}$ is a set of functions that correspond to state equations of the model, and ${\color{black}\chi}$ is the state-space model.

>>>>

		\citet{Bulley1984} suggests a process where the driving force for extraction is given by the difference between the concentration of the solute in bulk, $c_f$, and in the center of the pore, $c_p^*$. The concentration $c_p^*$ is in equilibrium with $c_s$ according to an equilibrium relationship. The rate of extraction is thus $r_e\left(c_f - c^*_p(c_s)\right)$. On the other hand, \citet{Reverchon1996} proposes a driving force given by the difference between $c_s$ and $c_p^*$. Concentration $c_p^*$ is determined by an equilibrium relationship with $c_f$ and the extraction rate given by Equation \ref{Model_kinetic_basic}

@@

		where $\Theta$ is a parameter space, ${\color{black}\bar{\phi}}$ is a set of functions that correspond to state equations of the model, and ${\color{black}\chi}$ is the state-space model.

### 2024-05-06 SFE_article_Parameter_Estimation_short_no_axial_diff- Chamomile/Short_no_axDiff_Supercritical_fluid_extraction_of_essential_oil_from_chamomile.tex
06.05

% ===================================================
% ABSTRACT
% ===================================================
\begin{abstract}
This study investigates the supercritical extraction process of essential oil from chamomile flowers.  Essential oils of chamomile are used extensively for medicinal purposes. Many different products of chamomile have been developed, the most popular of which is in the form of herbal tea. A distributed-parameter model describes the fluid-solid extraction process. The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions. The flow is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor. The physical properties of the solvent are estimated based on the Peng-Robinson equation of state. Model parameters, including the partition factor, internal diffusion coefficient, and decaying factor, were determined through maximum likelihood estimation based on experimental data assuming normally distributed errors. A set of laboratory experiments was performed under multiple constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \times 10^{-5}$ kg/s.

@@

Laboratory experiments were conducted by \citet{Povh2001} under various conditions to validate the model. The model parameters, such as partition factor, internal diffusion coefficient, and decaying factor, were determined through maximum likelihood estimation based on experimental data. The parameter space exploration revealed that while some parameters could be determined with a high degree of confidence, others, like the partition factor, had a low impact on the model's output. The identification of the low-impact parameters leads to model reduction. This work introduced a set of correlations to find a general relationship between parameters and the independent variables, which can be determined by operating conditions. The obtained correlations were introduced into the model and tested against the dataset.

>>>>

% ===================================================
% ABSTRACT
% ===================================================
\begin{abstract}
This study investigates the supercritical extraction process of essential oil from chamomile flowers. Essential oils of chamomile are used extensively for medicinal purposes. Many different chamomile products have been developed, the most popular of which is herbal tea. A distributed-parameter model describes the fluid-solid extraction process. The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions. The flow is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor. The physical properties of the solvent are estimated based on the Peng-Robinson equation of state. Model parameters, including the partition factor, internal diffusion coefficient, and decaying factor, were determined through maximum likelihood estimation based on experimental data assuming normally distributed errors. A set of laboratory experiments was performed under multiple constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \times 10^{-5}$ kg/s.

@@

Laboratory experiments were conducted by \citet{Povh2001} under various conditions to validate the model. The model parameters, such as partition factor, internal diffusion coefficient, and decaying factor, were determined through maximum likelihood estimation based on experimental data. The parameter space exploration revealed that while some parameters could be determined with a high degree of confidence, others, like the partition factor, had a low impact on the model's output. The identification of low-impact parameters leads to model reduction. This work introduced a set of correlations to find a general relationship between parameters and the independent variables, which can be determined by operating conditions. The obtained correlations were introduced into the model and tested against the dataset.
